The title

### 2019-07-26 README.Rmd
fixed pkg name in README.Rmd & knitted to md

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# hotspots

<!-- badges: start -->
[![Travis-CI Build Status](https://travis-ci.org/fboehm/hotspots.svg?branch=master)](https://travis-ci.org/fboehm/hotspots)

@@

The goal of hotspots is to analyze the Keller et al. (2018) expression trait hotspots.

@@

```{bash, docker_pull, eval = FALSE}
docker pull fjboehm/hotspots
```

@@

```{r, devtools_stuff, eval = FALSE}
install.packages("devtools")
devtools::install_github("fboehm/hotspots")
```

@@

```{r example}
#library(hotspots)
## basic example code
```

@@

Please note that the 'hotspots' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# qtl2hotspots

<!-- badges: start -->
[![Travis-CI Build Status](https://travis-ci.org/fboehm/qtl2hotspots.svg?branch=master)](https://travis-ci.org/fboehm/qtl2hotspots)

@@

The goal of qtl2hotspots is to analyze the Keller et al. (2018) expression trait hotspots.

@@

```{bash, docker_pull, eval = FALSE}
docker pull fjboehm/qtl2hotspots
```

@@

```{r, devtools_stuff, eval = FALSE}
install.packages("devtools")
devtools::install_github("fboehm/qtl2hotspots")
```

@@

```{r example}
#library(qtl2hotspots)
## basic example code
```

@@

Please note that the 'qtl2hotspots' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
